Mega-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2025-10-28 paper/1_Initial/manuscript.qmd
Summarize
@AnafNeves I think we can summarize the questionnaires list like that, without listing the scales details or item examples

      - bla bla

@@

<!-- Interoception Related -->
#### Interoception Related

The Multidimensional Assessment of Interoceptive Awareness Version-2 [MAIA-2, @mehling2018multidimensional] is a 37-item questionnaire assessing eight dimensions of interoception: Noticing, Not-Distracting, Not-Worrying, Attention Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust. Responses are rated on a 6-point Likert scale (e.g., “I notice when I am uncomfortable in my body”).

@@

The Bermond–Vorst Alexithymia Questionnaire [BVAQ, @vorst2001validity] consists of 40 items across five subscales: fantasising, identifying, analysing, verbalising, and emotionalising. Items are rated on a 5-point Likert scale. The BVAQ also provides two higher-order factors, namely affective and cognitive (e.g., “I like to tell others how I feel”).

>>>>

@@

#### Interoception

Interoception-related measures included the Multidimensional Assessment of Interoceptive Awareness Version-2 [MAIA-2, @mehling2018multidimensional], the Body Perception Questionnaire Short Form [BPQ-SF, @cabrera2018assessing], and the Interoceptive Confusion Questionnaire [ICQ, @brewer2016alexithymia]. We also included the Toronto Alexithymia Scale [TAS-20, @bagby1994twenty], and the Bermond–Vorst Alexithymia Questionnaire [BVAQ, @vorst2001validity], due to the close relationship between interoception deficits and alexithymia.
<!--
The Multidimensional Assessment of Interoceptive Awareness Version-2 [MAIA-2, @mehling2018multidimensional] is a 37-item questionnaire assessing eight dimensions of interoception: Noticing, Not-Distracting, Not-Worrying, Attention Regulation, Emotional Awareness, Self-Regulation, Body Listening, and Trust. Responses are rated on a 6-point Likert scale (e.g., "I notice when I am uncomfortable in my body").

@@

The Bermond–Vorst Alexithymia Questionnaire [BVAQ, @vorst2001validity] consists of 40 items across five subscales: fantasising, identifying, analysing, verbalising, and emotionalising. Items are rated on a 5-point Likert scale. The BVAQ also provides two higher-order factors, namely affective and cognitive (e.g., “I like to tell others how I feel”). -->
